Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-18 code/02-data-preparation.Rmd
pushing code to save for now (was just about to go on a run - need to improve upon later)

The discrepancy in the number of observations has led us to decide to train a new random forest model using the data provided by Heike where `flag == FALSE` (observations known to not have tank rash). The code for the random forest can be found in the document `paper.Rnw`.

>>>>

Current state of the code used to get to the right number of observations (need to clean up and document better and use in paper):

```{r}
read_csv("../data/raw/hamby-comparisons.csv.zip") %>%
  separate(land_id1, into = c("study1", "barrel1", "bullet1", "land1")) %>%
  separate(land_id2, into = c("study2", "barrel2", "bullet2", "land2")) %>%
  mutate(barrel1 = str_remove(barrel1, "Br"),
         bullet1 = str_remove(bullet1, "B"),
         land1 = str_remove(land1, "L"),
         barrel2 = str_remove(barrel2, "Br"),
         bullet2 = str_remove(bullet2, "B"),
         land2 = str_remove(land2, "L")) %>%
  mutate(bbl1 = factor(barrel1):factor(bullet1):factor(land1),
         bbl2 = factor(barrel2):factor(bullet2):factor(land2)) %>%
  filter(!(bbl1 %in% c("6:2:1", "9:2:4", "Unk:B:2", "Unk:Q:4") | 
           bbl2 %in% c("6:2:1", "9:2:4", "Unk:B:2", "Unk:Q:4"))) %>%
  dim()
```
